---
title: "Causeway_temp_sculpin"
author: "Peter Euclide"
date: "December 19, 2016"
output: html_document
---

```{r}

setwd("~/Dropbox/Genetics/Sculpin_analysis/Ontario_Data/Temp_Data")
library(ggplot2)
library(plyr)

```

```{r}
d <- read.csv("R_10727716_gut_drawbridge_Oct15-Oct16.csv", skip = 1)
d <- read.csv("R_10727717 Outer Mallets South July15-Oct16.csv", skip = 1)
d <- read.csv("R_10727711-outer mallets north Sept15-Oct16.csv", skip = 1)
d <- read.csv("R_10727718_SWCarryB_sept15-oct16.csv", skip = 1)
d <- d[,c(1:3)]
d$Date <- as.Date(d$Date, format = "%m/%d/%y")
min(d$Date, na.rm = T)
d <- subset(d, Date %in% c(min(d$Date, na.rm = T):(min(d$Date, na.rm = T)+365)))

dprf <- subset(d, Temp...C >9)
dhigh <- subset(d, Temp...C >=15)
nrow(as.data.frame(unique(dhigh$Date)))/365
nrow(as.data.frame(unique(dprf$Date)))/365

#"R_10727718_SWCarryB_sept15-oct16.csv"
#above 15=  0.3534247
#above 9 = 0.5561644

#outer mallets north Sept15-Oct16
# > nrow(as.data.frame(unique(dhigh$Date)))/365
# above 15= 0.3945205
# > nrow(as.data.frame(unique(dprf$Date)))/365
# above 9 = 0.5452055

# Outer Mallets South July15-Oct16
# > nrow(as.data.frame(unique(dhigh$Date)))/365
# above 15= 0.3890411
# > nrow(as.data.frame(unique(dprf$Date)))/365
# above 9= 0.5479452
# gut_drawbridge_Oct15-Oct16
# > nrow(as.data.frame(unique(dhigh$Date)))/365
# above 15= 0.3616438
# > nrow(as.data.frame(unique(dprf$Date)))/365
# above 9= 0.4931507

# > mean(abv15)
# [1] 0.3746575
# > sd(abv15)
# [1] 0.02017932
# 
# > sd(abv9)
# [1] 0.02869092
# > mean(abv9)
# [1] 0.5356165
